---
title: "GitHub Demonstration"
author: "Eduardo Martins"
date: "19/02/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(broom)
library(knitr)
ant <- read.csv("ant_data.csv") %>%
  mutate(zlat = (lat - mean(lat)) / sd(lat),
         zalt = (alt - mean(alt)) / sd(alt))
```

# Background

This is a demonstration of the use of GitHub for collaboration. In this R Markdown file, we will be analzying the ant dataset shown in the lecture about multiple regression.

# Data analysis

```{r correlation-plot, include = FALSE}
ggplot(ant, aes(x = lat, y = alt)) + 
  geom_point() +
  xlab("Degrees N Latitude") +
  ylab("Altitude (m)") +
  theme_bw()

cor.test(ant$lat, ant$alt)
```

The following model was fitted to the data:

$y_{i}\sim Normal \left (\mu_{i}, \sigma \right )$

$\mu_{i} = \beta_{0} + \beta_{lat}x_{lat,i} + \beta_{alt}x_{alt,i}$

where $y_{i}$ is the logarithm of the number of ant species at location $i$; $\beta_{0}$ is the model intercept; $\beta_{lat}$ and $\beta_{alt}$ are the model slopes for latitude and altitude, respectively; $x_{lat, i}$ and $x_{alt, i}$ are the latitude and altitude at location $i$; and $\sigma$ is the standard deviation of model residuals.

```{r multiple-regression, include = FALSE}
mlr <- lm(log10(spp) ~ lat + alt, data = ant)  
par(mfrow = c(1,3))
plot(mlr, which = 1:2)
hist(resid(mlr), xlab = "Residuals")
```

# Results

Here we would describe the results and refer to the model output and plots with observed data and fitted values.

```{r tables}
kable(tidy(mlr), col.names = c("Parameter", "Estimate", "SE", "t", "P-value"), 
      align = "cc", 
      caption = "Table 1. Estimates of intercept and slope.",
      digits= 2)
```


````{r fitted-plot, fig.cap = 'Figure 2. Relationship between the log number of ant species and latitude.'}
new_dat <- expand.grid(lat = seq(min(ant$lat), max(ant$lat), 0.1), 
                       alt = 0)

ci <- predict(mlr, newdata = new_dat, interval = "confidence")

pi <- predict(mlr, newdata = new_dat, interval = "prediction")

df <- data.frame(lat = new_dat$lat, 
                 alt = new_dat$alt,
                 fit = ci[, "fit"],
                 ci_lwr = ci[, "lwr"],
                 ci_upr = ci[, "upr"],
                 pi_lwr = pi[, "lwr"],
                 pi_upr = pi[, "upr"]) %>%
  mutate(lat = lat * sd(ant$lat) + mean(ant$lat),
         alt = alt * sd(ant$alt) + mean(ant$alt))

ggplot(ant, aes(x = lat, y = log10(spp))) +
  geom_point(colour = "red") +
  geom_line(data = df, aes(x = lat, y = fit)) +
  geom_line(data = df, aes(x = lat, y = ci_lwr), linetype = "dashed") +
  geom_line(data = df, aes(x = lat, y = ci_upr), linetype = "dashed") +
  geom_line(data = df, aes(x = lat, y = pi_lwr), linetype = "dotted") +
  geom_line(data = df, aes(x = lat, y = pi_upr), linetype = "dotted") +
  ylab("log10(S)") +
  xlab("Degrees N latitude") +
  theme_bw()
```


